---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This notebook shows how to use the monad ERTMon provided by this package.

# Set-up

Clear all R-session definitions:

```{r}
rm(list=ls())
```

Load the package from the GitHub repository:

```{r}
library(devtools)
install_github("antononcube/ERTMon-R")
library(ERTMon)
```


# Data ingestion

```{r}
dirName <- file.path( "..", "data", "FakeData")
dirName
```

## Event records

```{r}
fakeEventRecords <- read.csv( file = file.path( dirName, "eventRecords.csv"), stringsAsFactors = FALSE)
head(fakeEventRecords)
```

## Entity attributes

In order to run the underlying function

```{r}
fakeEntityAttributes <- read.csv( file = file.path( dirName, "entityAttributes.csv"), stringsAsFactors = FALSE)
fakeEntityAttributes
```

# Computation specification

Here we read the computation specification.

```{r}
fakeCompSpec <- read.csv( file = file.path( dirName, "computationSpecification.csv"), stringsAsFactors = FALSE)
fakeCompSpec
```

# Main pipeline

## Setting data

Initialize the monad and set the event records, entity attributes, and computation specification.

```{r}
ertmon1 <-
  ERTMonUnit() %>%
  ERTMonSetEventRecords( fakeEventRecords ) %>%
  ERTMonSetEntityAttributes( fakeEntityAttributes ) %>%
  ERTMonSetComputationSpecification( fakeCompSpec )
```


## Process event records

```{r}
ertmon1 <-
  ertmon1 %>%
  ERTMonProcessEventRecords()
```

```{r}
smats <- ertmon1 %>% ERTMonTakeContingencyMatrices()
names(smats)
```

## Examples of transformed matrices

```{r}
smats[["HR.Mean"]][1:12,]
```


# Plot the feature matrix

```{r}
image(ertmon1 %>% ERTMonTakeFeatureMatrix)
```

# Export the feature matrix

```{r}
ertmon1 %>% ERTMonExportToCSVFeatureMatrix( fileName = file.path( dirName, "featureMatrix.csv") )
```

