---
title: "Formula specification application example"
author: Anton Antonov
date: 2018-10-31
output: html_notebook
---

# Introduction

This notebook demonstrates the application of formula specification data frame onto a features matrix.

# The feature sub-matrices

Run the notebook "Event-records-transformations-main-use-case.Rmd" first. 
(Better with the parameter `categoricalMatricesQ` set to `FALSE`.)

Here we take the feature matrix (sparse) sub-matrices from data transformation object (`dtObj`):

```{r}
smats <- dtObj@sparseMatrices
```

# Specification

Here we make a fake formula specification for the fake medical data:

```{r}
formulaSpecDF <- 
  data.frame( "FeatureName" = c("HR.Mean", "HR.Range", "RR.Mean"), 
              "Coefficient" = c(1, 1, 1), 
              "Exponent" = c(1, 1, 2),
              "RatioPart" = c( "Numerator", "Denominator", "Denominator"),
              stringsAsFactors = FALSE)
formulaSpecDF
```

In order to apply the formula specification we have also choose a reduce function: "+" (summation) or "*" (multiplication).

Here is the interpretation:

$$formulaMat = \frac{reduceFunc[ \{ Coefficient[i] * smats[ FeatureName[i] ] ^ {Exponent[i]} : i \in NumeratorRows \} ]}{reduceFunc[ \{ Coefficient[i] * smats[ FeatureName[i] ] ^ {Exponent[i]} : i \in DenominatorRows \} ] }$$


# Application

The application of the formula specification is done with function `ApplyFormulaSpecification`.

```{r}
resMat <- ApplyFormulaSpecification( smats = smats[-length(smats)], formulaSpec = formulaSpecDF, reduceFunc = "+" )
```

```{r}
image(resMat)
```

