---
title: "Formula specification application example"
author: Anton Antonov
date: 2018-10-31
output: html_notebook
---

```{r}
library(dplyr)
library(Matrix)
library(ERTMon)
```

# Introduction

This notebook demonstrates the application of formula specification data frame onto a features matrix.

***The exposition has to be improved with easier to plot example results.***

# The feature sub-matrices

Run the notebook "Event-records-transformations-main-use-case.Rmd" first. 
(Better with the parameter `categoricalMatricesQ` set to `FALSE`.)

Here we take the feature matrix (sparse) sub-matrices from data transformation object (`dtObj`):

```{r}
fakeMon <-
  ERTMonUnit() %>% 
  ERTMonReadDataFromDirectory( "../data/FakeData/" ) %>% 
  ERTMonProcessEventRecords(echoStepsQ = FALSE)
```

```{r}
smats <- fakeMon %>% ERTMonTakeContingencyMatrices()
names(smats)
```

# Specification

Here we make a fake formula specification for the fake medical data:

```{r}
formulaSpecDF <- 
  data.frame( 
    "FormulaID" = c(1),
    "TermID" = c(1,1,1,2,2), 
    "TermCoefficient" = c( 0.5, 0.5, 0.5, 1.2, 1.2),
    "FeatureName" = c("HR.Mean", "NBP.M.Mean", "RR.Mean",  "NBP.M.Range", "NBP.M.Mean"),  
    "ReduceFunction" = c( "+", "+", "+", "*", "*"),
    "Coefficient" = c(1, 1, 1, 1, 1.6), 
    "Exponent" = c(1, 1, 2, 1, 1),
    "RatioPart" = c( "Numerator", "Denominator", "Denominator", "Numerator", "Denominator"),
    stringsAsFactors = FALSE)
formulaSpecDF
```

Each term in the formula specification has its own reduce function: "+" (summation) or "*" (multiplication).

Here is the interpretation (per term):

$$formulaMat = \frac{reduceFunc[ \{ Coefficient[i] * smats[ FeatureName[i] ] ^ {Exponent[i]} : i \in NumeratorRows \} ]}{reduceFunc[ \{ Coefficient[i] * smats[ FeatureName[i] ] ^ {Exponent[i]} : i \in DenominatorRows \} ] }$$


# Application

The application of the formula specification is done with function `ApplyFormulaSpecification`.

```{r}
fakeMon <- fakeMon %>% ERTMonComputeFormula( formulaSpec = formulaSpecDF )
resMat <- fakeMon %>% ERTMonTakeValue()
```

```{r}
image(resMat)
```

